API design for machine learning software: experiences from the scikit-learn project

### 2013-06-26 paper.tex
Clarify gensim paragraph.

Another package that deserves mention is the Gensim topic modeling toolkit
\citep{rehurek2010gensim},
which exemplifies API design for scalable processing of ``big data''.
Gensim's way of dealing with large datasets is to use algorithms
that have $O(1)$ space complexity and can be updated online.
The API is designed around the Python concept of an \textit{iterable}
(supported in the language by a restricted form of co-routines called
\textit{generators}).
While the text vectorization part of \sklearn
also uses iterables to some extent,
the emphasis is still on (mini-)batch processing,
even in the stateless, O(1) memory vectorizers
that implement the hashing trick of \citet{weinberger2009}.
This way of processing, as argued earlier in Section~\ref{sec:arrays},
reduces various forms of overhead
and makes effective use of the abundance of memory in modern computers.
We make no attempt to hide this batch-oriented processing from the user,
allowing control over the amount of memory actually dedicated
to \sklearn algorithms.

>>>>

Another package that deserves mention is the Gensim topic modeling toolkit
\citep{rehurek2010gensim},
which exemplifies API design for scalable processing of ``big data''.
Gensim's way of dealing with large datasets is to use algorithms
that have $O(1)$ space complexity and can be updated online.
The API is designed around the Python concept of an \textit{iterable}
(supported in the language by a restricted form of co-routines called
\textit{generators}).
While the text vectorizers part of \sklearn
also use iterables to some extent,
they still produce entire sparse matrices, intended to be used for batch or
mini-batch learning. This is the case
even in the stateless, O(1) memory vectorizers
that implement the hashing trick of \citet{weinberger2009}.
This way of processing, as argued earlier in Section~\ref{sec:arrays},
reduces various forms of overhead
and allows effective use of the vectorized operations provided by NumPy and 
SciPy.  We make no attempt to hide this batch-oriented processing from the user,
allowing control over the amount of memory actually dedicated
to \sklearn algorithms.
